Spectroscopic confirmation of very-wide stellar binaries and large-separation comoving pairs from \textsl{Gaia DR1}

### 2017-09-11 paper/comoving-followup.tex
between

\begin{abstract}
% Context
Members of widely-separated stellar binaries ($\gtrsim 0.1$~pc) or loosely bound
stellar associations and clusters are born with small spreads in kinematics and
chemistry, but disrupt and dissociate on timescales comparable to their orbital
time within the Milky Way.
The kinematic properties of comoving star pairs---bound wide binaries or unbound
but coeval stars---are therefore sensitive to both the smooth tidal field and
gravitational perturbation spectrum of the Milky Way.
% Aims
% Thus far, a few hundred confirmed comoving pairs with separations as large as
% $8~\pc$ have been discovered in the solar neighborhood using
% \project{Hipparcos} astrometry combined with radial velocity surveys.
In previous work, we identified $>4,000$ candidate comoving pairs using only
astrometric data from the Tycho-Gaia Astrometric Solution (TGAS) catalog and
find a large number of pairs with separations $\gtrsim 1~\pc$.
Without radial velocity measurements for the vast majority of these pairs, the
false-positive rate at these separations is significant ($\sim 50\%$).
% Methods
Here we present results from our own low-resolution radial-velocity survey of a
random sample of the candidate pairs to identify and validate true comoving star
pairs.
% Results
Of the \npairsobs\ observed comoving pairs, we confirm \ncomoving\ comoving
pairs with separations as large as $\approx 10~\pc$, our original search limit.
At separations of $10^{-3}~\pc$ to $\approx 0.5~\pc$,
the number of confirmed pairs per separation decreases with increasing
separation (number per log separation is uniform).
From $\approx 0.5~\pc$ to $10~\pc$, the number per separation is approximately
uniform (number per log separation increases).
% Conclusions
We confirm the discovery of a population of comoving star pairs at very large
separations, suggesting that disrupted wide binaries and stellar associations
remain approximately spatially coherent.
\end{abstract}

>>>>

\begin{abstract}
% Context
Members of widely-separated stellar binaries ($\gtrsim 0.1$~pc) or loosely bound
stellar associations and clusters are born with small spreads in kinematics and
chemistry, but disrupt and dissociate on timescales comparable to their orbital
time within the Milky Way.
The kinematic properties of comoving star pairs---bound wide binaries or unbound
but coeval stars---are therefore sensitive to both the smooth tidal field and
gravitational perturbation spectrum of the Milky Way.
% Aims
% Thus far, a few hundred confirmed comoving pairs with separations as large as
% $8~\pc$ have been discovered in the solar neighborhood using
% \project{Hipparcos} astrometry combined with radial velocity surveys.
In previous work, we identified $>4,000$ candidate comoving pairs using only
astrometric data from the Tycho-Gaia Astrometric Solution (TGAS) catalog and
find a large number of pairs with separations $\gtrsim 1~\pc$.
Without radial velocity measurements for the vast majority of these pairs, the
false-positive rate at these separations is significant ($\sim 50\%$).
% Methods
Here we present results from our own low-resolution radial-velocity survey of a
random sample of the candidate pairs to identify and validate true comoving star
pairs.
% Results
Of the \npairsobs\ observed comoving pairs, we confirm \ncomoving\ comoving
pairs with separations as large as $\approx 10~\pc$, our original search limit.
Between separations of $10^{-3}~\pc$ to $\approx 0.5~\pc$,
the number of confirmed pairs per separation decreases with increasing
separation (number per log separation is uniform).
From $\approx 0.5~\pc$ to $10~\pc$, the number per separation is approximately
uniform (number per log separation increases).
% Conclusions
We confirm the discovery of a population of comoving star pairs at very large
separations, suggesting that disrupted wide binaries and stellar associations
remain approximately spatially coherent.
\end{abstract}
